Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-22 ms/main.tex
revise fig 5 legend

%%% Figure: coexistence map - with oblique transmission
\begin{figure}[htb]
  \centering
  \includegraphics{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  The orange curve for wich the polymorphic equilibrium is stable is given by  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_with_oblique}
  \end{figure}
\pagebreak

>>>>

%%% Figure: coexistence map - with oblique transmission
\begin{figure}[htb]
  \centering
  \includegraphics{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_with_oblique}
  \end{figure}
\pagebreak
